\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
\textbf{{\huge SATVIK TIWARI}}
\end{center}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \href{https://www.linkedin.com/in/satviktiwari/}{LinkedIn: linkedin.com/satviktiwari/} & 
  Email: \href{mailto:satviktiwari.ec19@rvce.edu.in}{satviktiwari.ec19@rvce.edu.in}\\
  \href{https://satviktiwari.netlify.app}{Portfolio: satviktiwari.netlify.app}  & 
  Mobile: +91-9098412228 \\
  \href{https://github.com/satviktiwari}{GitHub: github.com/satviktiwari} &
  \href{https://drive.google.com/file/d/1LQlHFQqkuVfjBgQ2uICyUJPpx2jUVdDT/view?usp=sharing}{Coding Profiles: Click-Here} \\ 
  Certifications: \href{https://drive.google.com/file/d/1i43F2_F_sFLirghEWX-SV7maJ8NU8jX7/view?usp=sharing}{Click-Here} \\ 
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RV College of Engineering}{Bangalore, India}
      {Bachelor of Engineering - Electronics and Communication;  CGPA: 8.85}{August 2019 - July 2023}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Data Structures and Algorithms, Database Management System, Computer Networks, Signal Processing and Machine Learning}}}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Kylo Apps}{Remote}
    {React Developer Intern}{Jan 2022 - Mar 2022}
    \resumeItemListStart
        \resumeItem{Work}
          {Worked on the development of UI components for React Applications. Built reusable UI components for multiple Web Applications and worked on the re‑building and functional modifications of existing Applications.}
          \newline
      \resumeItemListEnd

\vspace{-5pt}
    \resumeSubheading
		{Wipro-IISc Research and Innovation Network}{Bangalore, Karnataka}
		{Software Development and Machine Learning Intern
}{Sep 2021 -  Feb 2022}
		\resumeItemListStart
        \resumeItem{Work}{Worked on the development of Control Systems for Autonomous Vehicle. Developed a Virtual Simulator to simulate car controls using the keyboard. Developed ML‑powered software tool to generate collision free Optical Flow Path for Autonomous Vehicles using OpenCV.}
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{FRAMEWORK FOR CCTV STORAGE OPTIMIZATION}{ Developed an algorithm and website to optimize the storage
space of CCTV recordings using the YOLO‑v3 algorithm and
OpenCV library by removing the redundant CCTV footage
frames having Euclidean distance lesser than a threshold
value. The algorithm efficiently reduced the storage space by
76\% of the existing space without any compromise on the
quality of the recordings. 
\newline
Tech: HTML, CSS, JavaScript, Python, Firebase, OpenCV
\newline
\href{https://github.com/satviktiwari/CCTV-Storage-Optimization}{GitHub Repository: Click Here}~~~~ \href{https://cctvframework.netlify.app/}{Live Deployment: Click Here}}
\vspace{2pt}
\resumeSubItem{SAG MEASUREMENT AND CIRCLE FITTING ALGORITHM}{Programmed an Algebraic Circle Fitting Algorithm for sag measurement in pipes and fuel rods using Image Analysis of diffracted laser beams. Developed program for sag
measurement with respect to the slope of coordinates of the
laser beam and the output screen
\newline
Tech: C++, Python, MATLAB, Image, OpenCV
\newline 
\href{https://github.com/satviktiwari/Circle-Fitting-and-Sag-Measurement}{GitHub Repository: Click Here}}
\vspace{2pt}
\resumeSubItem{SUS MAFIA}{Developed a platform for Sus Mafia NGO to recruit volunteers. Incorporated user-side \& company-side registration, candidate profile viewing feature, real-time chat application and candidate leader board functionality in the application. Added blog writing feature in the application. The project was awarded Runner-Up position in JPMorgan Chase \& Co. Code for Good 2022 event.   
\newline
Tech: HTML, CSS, JavaScript, React JS, Node JS, Express, MongoDB, Firebase
\newline
\href{https://github.com/satviktiwari/CRUD-Application}{GitHub Repository: Click Here}}
\vspace{2pt}
\resumeSubItem{COVID DETECTION TOOL}{ Developed a website for symptoms‑based COVID detection
and apython application for chest x‑ray scan‑based COVID
detection. Used CNN algorithm for Image Processing of
x‑ray scan. Used Naïve Bayes classifier for
symptoms‑based detection and programmed in JavaScript.
\newline
Tech: HTML, CSS, JavaScript, Python
\newline
\href{https://github.com/satviktiwari/COVID-Detection-Tool}{GitHub Repository: Click Here}~~~~ \href {https://covid19-detection.netlify.app}{Live Deployment: Click Here}}
\vspace{2pt}
\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------SKILLS-----------------
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Programming Languages}{ C, C++, Python}
	\resumeSubItem{Web Development}{ HTML, CSS, JavaScript, ReactJS, NodeJS, Express}
	\resumeSubItem{Database}{ MySQL, MongoDB, Firebase}
	\resumeSubItem{Miscellaneous}{ Git, GitHub, Netlify, Latex, VS Code}
	\resumeSubItem{Soft Skills}{ Problem Solving, Design Thinking, Public Speaking, Team Work, Leadership, Decision Making}

\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Programming Profiles}
\begin{description}[font=$\bullet$]
\item {LeetCode: 3-star profile, 1592 rating (max), 4 batches earned, 600+ problems solved with nearly 70\% accuracy.}
\vspace{-5pt}
\item {Geeks for Geeks: 4th rank in RVCE GFG Portal among 3000+ coders, 600+ problems solved, 1750 GFG Score.}
\vspace{-5pt}
\item {CodeChef: 3-star profile, 1693 rating, secured 130 rank in CodeChef Long Challenge 2022 among 15852 participants.}
\end{description}
\vspace{-5pt}
%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {Runners‑Up at Code for Good‑2022 hackathon organized by JP Morgan Chase \& Co. (June 4‑5, 2022)}

\end{description}

\vspace{-5pt}
\section{Certifications}
\begin{description}[font=$\bullet$]
\item {Python Data Structures (Coursera)}
\vspace{-5pt}
\item {Problem Solving Basic and Intermediate (HackerRank)}
\vspace{-5pt}
\item {The Joy of Computing using Python (NPTEL)}
\vspace{-5pt}
\item {SQL Programming (HackerRank)}
\end{description}

\end{document}
